Flowchart of Current Algorithm

### 2009-04-24 docs/flowchart/flowchart.tex
more detailed notes (in red) about proposed changes to Advect Base Pressure Spherical

@@

\item Update $p_0$ and compute $\psi$.
\begin{description}
\item For plane-parallel,\\
{\bf Advect Base Pressure Planar}$[p_0^n, w_0^{\nph}, \etarho^{n+\myhalf}]$ 
$\rightarrow [p_0^{n+1},\psi^{\nph}]$.
\item For spherical,\\
{\bf Advect Base Pressure Spherical}$[p_0^n,w_0^{\nph},\gammabar^{n+1,*},\overline{S^{\nph,\star}}] \rightarrow [p_0^{n+1},\psi^n,\psi^{\nph}]$.
\end{description}
\MarginPar{Rework Advect Base Pressure Spherical to take time-centered $\gammabar$?  Also, look at how $\psi^n$ is computed.  The base time centering doesn't make sense.}

>>>>

\begin{color}{red}
Andy's proposal: We need to pass in two different $\gammabar$ objects, $\gammabar^{\inp,n}$ and $\gammabar^{\inp,n+\myhalf}$.  The pressure update will use $\gammabar^{\inp,n+\myhalf}$.  To compute $\psi^{\outp,n}$, we use $\gammabar^{\inp,n}$.  To compute $\psi^{\outp,n+\myhalf}$, we use $\gammabar^{\inp,n+\myhalf}$.  In the first half of the algorithm, we pass in $\gammabar^n$ for both arguments.  For the second half of the algorithm, we pass in $\gammabar^n$ and $(\gammabar^n+\gammabar^{n+1,*})/2$.  I don't think we ever need $\gammabar^{(1)}$, as the only place it's currently used is as an input to the first call to {\bf Advect Base Pressure Spherical}.
\end{color}

@@

\item Update $p_0$ and compute $\psi$.
\begin{description}
\item For plane-parallel,\\
{\bf Advect Base Pressure Planar}$[p_0^n, w_0^{\nph}, \etarho^{n+\myhalf}]$ 
$\rightarrow [p_0^{n+1},\psi^{\nph}]$.
\item For spherical,\\
{\bf Advect Base Pressure Spherical}$[p_0^n,w_0^{\nph},\gammabar^{n+1,*},\overline{S^{\nph,\star}}] \rightarrow [p_0^{n+1},\psi^n,\psi^{\nph}]$.
\end{description}
